### 2018-02-20 results.Rnw
Minimum comments.
unsure

<<message=FALSE>>=
library(damr)      # input DAM2 data
library(zeitgebr)  # periodogram computation
library(sleepr)    # sleep analysis
library(ggetho)    # behaviour visualisation
@

@@

<<cache=TRUE>>=
metadata <- link_dam2_metadata("metadata.csv", ".")   # linking
# print(metadata)                                     # check metadata
dt <- load_dam2(metadata)                             # loading
summary(dt)                                           # quick summary
@

>>>>

<<message=FALSE>>=
library(damr)      # input DAM data
library(zeitgebr)  # periodogram computation
library(sleepr)    # sleep analysis
library(ggetho)    # behaviour visualisation
@

@@

<<cache=TRUE>>=
metadata <- link_dam_metadata("metadata.csv", ".")   # linking
# print(metadata)                                     # check metadata
dt <- load_dam(metadata)                             # loading
summary(dt)                                           # quick summary
@
